animbook: Visualizing changes in performance measures and demographic affiliations using animation

### 2023-10-24 animbook-journal.Rmd
animation added
pdf version of figure now sized

---
title: "animbook: Visualizing changes in performance measures and demographic affiliations using animation"
date: 04/09/2023
abstract: >
  An abstract of less than 150 words.
draft: true
author:  
  - name: Krisanat Anukarnsakulchularp
    affiliation: Monash University
    address:
    - Faculty of Business and Economics
    - Melbourne, Australia
    orcid: 0009-0008-5638-7124
    email:  kanu0003@student.monash.edu
type: package
output: 
  rjtools::rjournal_web_article:
    self_contained: yes
    toc: no
bibliography: animbook-journal.bib

@@

```{r data-diagram, fig.cap="The data transformation diagram."}
knitr::include_graphics("figures/data-diagram.png")
```

@@

>>>>

---
title: "animbook: Visualizing changes in performance measures and demographic affiliations using animation"
date: 04/09/2023
abstract: >
  An abstract of less than 150 words.
draft: true
author:  
  - name: Krisanat Anukarnsakulchularp
    affiliation: Monash University
    address:
    - Faculty of Business and Economics
    - Melbourne, Australia
    orcid: 0009-0008-5638-7124
    email:  kanu0003@student.monash.edu
type: package
output: 
  rjtools::rjournal_article:
    self_contained: yes
    toc: no
bibliography: animbook-journal.bib

@@

```{r data-diagram, fig.cap="The data transformation diagram.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page"}
knitr::include_graphics("figures/data-diagram.png")
```

@@

```{r dwchange-gif, out.extra="class = 'gif'", fig.cap = "Something", eval=knitr::is_html_output()}
knitr::include_graphics("figures/dwchange.gif")
```
